---
title: 'Part 1: Time series wrangling'
author: "Anna Talken"
date: "2/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tsibble)
library(feasts)
library(fable)
library(here)
```

## Read in the data and convert to tsibble
```{r}
energy <- read_csv(here("data", "energy.csv"))

energy_ts <- energy %>% 
  mutate(date = tsibble::yearmonth(month)) %>% 
  as_tsibble(key = NULL, index = date)
```

## Exploratory time series visualization 

```{r}
ggplot(data = energy_ts, aes(x = date, y = res_total)) +
  geom_line() +
  labs(y = "Residential energy consumption \n (Trillion BTU)")
```
### Seasonplot
```{r}
energy_ts %>% 
  gg_season(y = res_total) +
  theme_minimal() +
  labs(x = "month", 
       y = "residential energy consumption (trillion BTU)")
```
### Subseries plot
```{r}
energy_ts %>% 
  gg_subseries(res_total)
```
### Decomposition by STL

```{r}
#Find STL decomposition
dcmp <- energy_ts %>% 
  model(STL(res_total ~ season()))

#View the components
components(dcmp)

#Visualize the components
components(dcmp) %>% 
  autoplot() +
  theme_minimal()
```
### Autocorrelation function
```{r}
energy_ts %>% 
  ACF(res_total) %>% 
  autoplot()
```
## Forecasting by Holt-Winters exponential smoothing

```{r}
# Create the model
energy_fit <- energy_ts %>% 
  model(
    ets = ETS(res_total ~ season("M"))
  )

#Forecasting using the model 10 years into the future
energy_forecast <- energy_fit %>% 
  forecast(h = "10 years")

#Plot just the forecasted values (with 80 and 95 CIs)
energy_forecast %>% 
  autoplot()

#plot forecast added to the original data
energy_forecast %>% 
  autoplot(energy_ts)
```
### Assessing the residuals

```{r}
# USe broom augment function to predict values and residuals
energy_predicted <- broom::augment(energy_fit)

#Use View(energy_predicted) to see resulting data frame

View(energy_predicted)
```

Now plot the energy values(res_total) and the predicted values (sotred as .fitted)

```{r}
ggplot(data = energy_predicted) + 
  geom_line(aes(x = date, y = res_total)) +
  geom_line(aes(x = date, y = .fitted), color = "red")
```

Explore the residuals (should be uncorrelated, centered at 0 and normally distributed)

```{r}
ggplot(data = energy_predicted, aes(x = .resid)) +
  geom_histogram()
```











